Highlighting Disputed Claims on the Web

### 2009-10-31 papers/www_disputefinder/disputefinder.tex
Did a polishing pass over the paper

We describe Dispute Finder, a browser extension that alerts a user when information they read online is disputed by a source that they might trust. Dispute Finder examines the text on the page that the user is browsing and highlights any phrases that appear to entail claims in its database of known disputed claims. If a user clicks on a highlighted phrase then Dispute Finder shows them a summary of articles that support other points of view.

Dispute Finder builds its database of disputed claims by crawling web sites that already maintain lists of disputed claims, and by allowing users to enter claims that they believe are disputed. Dispute Finder identifies instances of disputed claims by running a simple textual entailment algorithm inside the browser extension, referring to a cached local copy of a subset of our claim database.

@@

In recent years, we have seen the emergence of a new class of applications that help users recognize and make sense of online dispute. In this paper, we describe Dispute Finder, an application that alerts a user when information they read online is disputed by a source that they might trust.

%The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}. If a user is to gain a broad understanding of a topic then they will need to either spend time searching for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information. Even when a user spends time investigating every claim that they think might be disputed, they can still be misled by information that they had not realized was disputed.

@@

A user can install Dispute Finder as an extension to the Firefox\footnote{http://www.mozilla.org/firefox} web browser. When installed Dispute Finder will highlight snippets of text that make disputed claims (Figure~\ref{highlight}). 
If a user clicks on a highlighted snippet, Dispute Finder will show articles that put forward different points of view,  each of which is from a source we believe the user is likely to trust (Figure~\ref{claimview}).

Dispute Finder consists of a server-side database and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web. A disputed claim is a statement about the world that some people disagree with. For example ``global warming is a hoax'', ``gun control will reduce crime'', ``eskimos have many words for snow'', or ``margarine is healthier than butter''. A claim can be stated in many ways. For example ``margarine is healthier than butter'' and ``butter is worse for you than margarine'' are paraphrases of the same claim. For each claim, the database contains references to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}).

The browser extension maintains its own local copy of the database, and scans the text on the current page for text snippets that appear to {\it entail} a claim. A snippet is a continuous region of text on a web page. A snippet is defined to entail a claim if a normal user reading that snippet would reasonably conclude that the author of the page believed the claim was true. For example ``the english have as many words for rain as the eskimos have for snow'' {\it entails} ``eskimos have many words for snow'', even though this claim is never stated explicitly.

@@

If users are going to adopt Dispute Finder, it is important that it provides users with a service that they feel will be of benefit to them, and has an interface that they can use. We used interviews to construct two personas, which model the two ways that we expect a user to use Dispute Finder.

{\it Skeptical Readers} want to know when something they read is disputed by a source that they might trust. They are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic. A user may behave like a skeptical reader for some topics and not others. For example a user may be skeptical when reading about topics that affect them (e.g. health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that do not affect them (e.g. entertainment).

{\it Activists} care strongly about particular issues and are prepared to spend some time helping others know that something that they disagree with is disputed. They are the same kinds of people who join protest groups, write blogs, email news stories, or argue about topics online. They are motivated by a desire to influence others and to gain status by being seen to do so. A user is likely to be an activist on some issues, but not for others. An activist will often also be a skeptical reader.

Many users fall into neither of these two personas. If a user does not regularly read information online that they feel they need to need to understand well, or restricts their reading to sources that they believe they can trust, then they are unlikely to be interested in Dispute Finder.

@@

According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust. Their 2008 survey found that 33\% of Democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says. Similarly, 51\% of Democrats regularly watch CNN, and yet only 35\% believe all or most of what CNN says. While these figures covered TV, rather than the web, Pew report that 48\% of web users people regularly follow search links to unfamiliar sources, and that users view online sources such as blogs with more skepticism that their print, broadcast, and cable counterparts.

These findings were backed up by our interviews (Section~\ref{sec:interviews}). Several participants told us that they regularly get information from sources that they do not entirely trust. A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search. For example they might read Michael Moore because he is entertaining, or read articles mailed to them by friends.

@@

There is also evidence that a significant group of people are interested in checking information they read on the web. Several sites exist that a user can use to investigate a claim that they have read elsewhere on the web. Snopes.com contains information about urban myths such as ``eskimos have many words for snow''. Factcheck.org and Politifact.com investigate claims about US politics. According to Quantcast.com, Snopes has around five million unique visitors per month, FactCheck almost a million, and Politifact about three hundred thousand. Although these numbers are not huge compared to the really big sites, there are many other sites that people can use to check facts and so the real number of users who regularly check facts online is likely to be much higher.

To check our assumptions, we circulated a survey among members of a local debate club, who we anticipated would be a good match for our Skeptical Reader and Activist personals. Of the 23 people who responded, 91\% said that they sometimes or often check information they read on a trusted site (64\% often, 27\% sometimes) and 91\% said that they sometimes of often check information by searching for other web pages about the same topic (74\% often, 17\% sometimes).

@@

Dispute Finder is designed to deal primarily with cases where a user is not aware that the information they are reading is disputed and so does not realize that they should check it on one of these services. Dispute Finder is designed to work together with fact checking sites. Indeed Dispute Finder automatically imports disputed claims and opposing articles from Snopes and Politifact.

@@

Rather than allowing a user to directly express their own opinions about a topic, Dispute Finder instead requires a user who wants to promote a particular opinion to do so by linking to an article from a trusted source that argues for that opinion. Our interviews (Section~\ref{sec:interviews}) lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.

Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate {\it text on a particular page} while Dispute Finder attempts to allow a user to annotate a {\it general claim, everywhere it appears on the web, however it is worded}. If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page. If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears. The closest annotation system to Dispute Finder is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.

Several Sensemaking, Decision Support, and Argumentation tools allow a user to annotate a document with structured information that they may then share with other users. TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that have been extracted from them, and connecting these facts into a decision graph. ClaimSpotter~\cite{Sereno2005,Sereno2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document. Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts about it. Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''. An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.

@@

There are also several tools that find pages that put forward different points of view, rather than identifying disputed claims within a page. News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story. The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue. 
Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias. Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking. Newstrust allows users to rate news articles for quality and objectivity.

@@

\item[Highlighting disputed claims for users:] If we are to alert a user when they are encountering disputed information, we need to be able to tell what information they are encountering, and be able to alert them when information they encountered was disputed. Ideally, this method should apply to as much of the information the user encounters as possible, and be easy for a user to adopt. We also want to avoid distracting the user unnecessarily, while also making sure that they do notice disputed claims that they would care about.

\item[Providing tools that help users interpret disputed claims:] Once a user has learned that a claim is disputed, it is likely that they will want to see information that will help them decide whether they should believe the claim. We want to help a user understand both {\it who} holds other points of view and {\it why} other people hold different points of view.

\item[Determining Trustworthy Sources:] What sources should we consider ``trustworthy'' in the sense that they opinions are worth presenting to the user, and we should inform the user when a trustworthy source disagrees with what they are reading. There is a trade-off between showing a user sources that they will trust, and showing them sources that will expose them to a new point of view.

\end{description}

These challenges are not unique to dispute finder. They apply to any tool that informs a user about disputed information and helps users interpret this disputed information.

In the rest of this section, we explain the various alternative solutions for each of these problems, and our experiences with the different approaches that we implemented and tested.

@@

Dispute Finder maintains a shared database of known disputed claims. The browser extension highlights a text snippet if it believes that the snippet entails one of the claims in this database (Figure~\ref{snippet_claim_article}). Claims can either be added directly by users (Figure~\ref{add_claim}) or mined from web sites such as Snopes and Politifact that already maintain well curated databases of disputed claims,

This database should not contain contain everything that has ever been disputed by anyone. In some sense almost everything is disputed by someone on the web. There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would would be so distracting as to be worthless. Similarly, there is little point spending effort rebutting claims that nobody believes. For example there is reliable evidence opposing the claim that the moon is made of cheese, but few people believe this claim is true. What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.

@@

We also provide users means to add their own disputed claims using the Dispute Finder web interface (Figure~\ref{add_claim}). The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org. It first encourages the user to search the existing database to see if their claim already exists, and then allows them to create a new claim. When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing article.

The automatic import bootstraps Dispute Finder with a large database of disputed claims without needing a large active user community, and the crowd-sourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.

@@

In future work, we hope to automatically find disputed claims on the web by looking for phrases like ``falsely claimed that X'' --- a similar techniques to that used by Hearst to find hyponyms~\cite{Hearst1992}.

@@

To highlight disputed snippets on a web page, Dispute Finder needs to be able to determine when a snippet entails the truth of a known disputed claim. This is complicated by the fact that a claim can be phrased many different ways, and a snippet does not need to explicitly state a claim in order to entail its truth. For example ``I prefer margarine to butter because it is healthier'' entails ``margarine is healthier than butter''. Our implementation maintains a local copy of our claim database inside the browser extension and runs a simple textual entailment algorithm inside the browser to look for sentences that appear to entail known disputed claims.

There is a trade-off between precision and recall. We want to maximize the likelihood that Dispute Finder will highlight a snippet if it is making a known disputed claim, while minimizing the likelihood that it will highlight a snippet that is not making a known disputed claim.

We implemented and tested four different approaches that represent different points along this trade-off:

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/mark_disputed.png}
	\caption{Explicit page marking: select the text that makes a disputed claim and click ``this is disputed'' from the context menu.}
	\label{mark_disputed}
	\end{center}
\end{figure}

@@

\begin{description}
\item[Explicit page marking:] The user explicitly marks a snippet on a page by selecting the snippet, and selecting ``mark as disputed'' from a context menu (Figure~\ref{mark_disputed}).

\item[Bulk page marking:] The user uses a search interface to rapidly gather a large number of snippets that contain similar phrases, and then marks them in bulk. The server uses Yahoo BOSS\footnote{http://developer.yahoo.com/search/boss} to search the web for snippets that resemble a paraphrase entered by the user. The user then selects all the snippets that they would like to mark (Figure~\ref{training}).

\item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier. We used a simple Bayesian classifier with n-grams as features. This classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.  Once the classifier has been trained, the server uses it to refine which of the rest of the results from Yahoo BOSS should be marked (Figure~\ref{training}).

@@

Explicit page marking has the highest precision, but the poorest coverage. Since a user is looking at the page in its entirety, they can read the snippet in context and make a good judgment about whether the snippet is indeed making the claim. However the manual effort required per page makes it difficult for this approach to scale. We also found that it can also be hard to motivate a user to mark snippets if they think that it is unlikely that another user with the Dispute Finder extension will read exactly this page. This same problem that has hindered the adoption of numerous web page annotation tools.

@@

Client side entailment gets the most coverage. Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined. This is particularly important for news pages, which are frequently read only a few minutes after they are posted. Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and information on an intranet.

A further advantage of the client-side approach is that it avoids the need for the client to give the server any information about what pages the user is browsing. The list of all URLs and snippets that make disputed claims is too large and updates too frequently for it to be practical for the client to store it locally, so the client instead asks the server for information about each URL the user browses, reducing user privacy. By contrast, the list of paraphrases is small enough and changes slowly enough that the client can maintain its own local copy of the database, removing the need for the client to tell the server what pages the user is browsing.

@@

LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist. Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, inferring inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using Bayesian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}. Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions. Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.

@@

Other authors have used similar algorithms to find repeated information on the web. Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagiarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}. MemeTracker~\cite{Backstrom2009} looks for phrases shared by multiple news stories, accounting for minor variations, and uses this to track the way that news flows between traditional news sources and blogs.

@@

The Dispute Finder Firefox extension uses two mechanisms to inform a user when information on the page they are reading is disputed. It highlights any snippets that make the disputed claims in red, and it displays a notification bar (Figure~\ref{highlight_bar}).

The notification bar alerts the user that they should look out for highlighted snippets. Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors.} or if the user is color blind. The notification bar also allows a user to step through the highlighted snippets on the page.

The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims. This allows a user to ignore disputed claims that are made by text that the user is not interested in - such as user comments. The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it is not making. In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the ``report incorrect highlighting'' button from the popup interface.

@@

When a user clicks on a highlighted snippet, Dispute Finder displays a popup pane with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read. In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{article_list}). We also implemented and tested an interface that contained a user-editable argumentation graph, however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.

@@

\begin{description}
\item[Convenience:] A user may not have the patience to search for a good source of information about a claim. 
\item[Moderation:] We only want Dispute Finder to highlight a claim if we know that there is credible evidence for an alternative point of view - otherwise Dispute Finder would be annoying. By storing the evidence for alternative points of view inside Dispute Finder, it becomes easier for a moderator user to evaluate whether a claim is sufficiently disputed that it belongs in the Dispute Finder database.
\item[Filtering:] Although we have not implement this feature currently, we think it could be useful to build a model of what sources a user trusts and only highlight a disputed claim if a source that the user trusts argues against it.
\end{description}

Naturally, sources such as Wikipedia, Politifact, and Snopes are often used as sources of evidence for and against a claim --- indeed we currently import articles from Politifact and Snopes automatically.

@@

\begin{description}
\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph inspired by IBIS~\footnote{Issue Based Information System} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}. Each claim is linked to claims that represent alternative points of view, and claims that support that point of view. Each claim also has a list of articles that argue in favor of that claim (Figure\ref{popup_graph})

@@

\section{Evaluation}
\label{sec:interviews}

>>>>

We describe Dispute Finder, a browser extension that alerts a user when information they read online is disputed by a source that they might trust. Dispute Finder examines the text on the page that the user is browsing and highlights any phrases that resemble known disputed claims. If a user clicks on a highlighted phrase then Dispute Finder shows them a list of articles that support other points of view.

Dispute Finder builds a database of known disputed claims by crawling web sites that already maintain lists of disputed claims, and by allowing users to enter claims that they believe are disputed. Dispute Finder identifies snippets that make known disputed claims by running a simple textual entailment algorithm inside the browser extension, referring to a cached local copy of the claim database.

@@

The web contains a huge amount of information, but some of this information is factually incorrect and some sites present only one side of a contentious issue~\cite{Herman2002}. If a user is to gain a broad understanding of a topic then they will need to either spend time searching for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information. Even when a user spends time investigating every claim that they think might be disputed, they can still be misled by information that they had not realized was disputed.

In recent years, we have seen the emergence of a new class of tools that help users recognize and make sense of disputed information on the web. In this paper, we describe Dispute Finder, a tool that alerts a user when a web page they are reading appears to be making a claim that is disputed by a source that they might trust.

@@

A user can install Dispute Finder as an extension to the Firefox\footnote{http://www.mozilla.org/firefox} web browser. When installed Dispute Finder will highlight snippets of text that make disputed claims (Figure~\ref{highlight}). 
If a user clicks on a highlighted snippet, Dispute Finder will show articles that put forward alternative points of view,  each of which is from a source we believe the user might trust (Figure~\ref{claimview}).

Dispute Finder consists of a server-side database and a Firefox browser extension. The database contains a set of known disputed claims that frequently appear on the web. A disputed claim is a statement about the world that some people disagree with. For example ``global warming is a hoax'', ``gun control will reduce crime'', ``Eskimos have many words for snow'', or ``margarine is healthier than butter''. A claim can be stated in many ways. For example ``margarine is healthier than butter'' and ``butter is worse for you than margarine'' are {\it paraphrases} of the same claim. For each claim, the database contains links to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}).

The browser extension maintains its own local copy of the database, and scans the text on the current page for text snippets that appear to {\it entail} a claim. A snippet is a continuous region of text on a web page. A snippet is considered to {\it entail} a claim if a typical user reading that snippet would reasonably conclude that the author of the page believed the claim was true. For example ``the English have as many words for rain as the Eskimos have for snow'' {\it entails} ``Eskimos have many words for snow'', even though this claim is never stated explicitly.

@@

If users are going to adopt Dispute Finder, it is important that it solves a real need. We used interviews to construct two personas which model the two ways that we expect a user to use Dispute Finder.

{\it Skeptical Readers} want to know when something they read is disputed by a source that they might trust. They are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic. A user will typically behave like a skeptical reader for some topics and not others. For example a user may be skeptical when reading about topics that affect them (e.g. health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that do not affect them (e.g. entertainment).

{\it Activists} care strongly about particular issues and are prepared to spend some time informing others that something that they disagree with is disputed. They are the same kinds of people who join protest groups, write blogs, email news stories, or argue about topics online. They are motivated by a desire to influence others and to gain status by being seen to do so. A user is likely to be an activist on some issues, but not on others. An activist will often also be a skeptical reader.

Many users fall into neither of these two personas. If a user does not regularly read information online that they feel they need to need to understand well, or restricts their reading to sources that they believe they can trust, then they are unlikely to be interested in a tool like Dispute Finder.

@@

According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust. Their 2008 survey found that 33\% of Democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says. Similarly, 51\% of Democrats regularly watch CNN, and yet only 35\% believe all or most of what CNN says. While these figures are for TV News, rather than the web, Pew report that 48\% of web users people regularly follow search links to unfamiliar sources, and that users view online sources such as blogs with more skepticism that their print, broadcast, and cable counterparts.

These findings were backed up by our interviews (Section~\ref{sec:interviews}). Several participants told us that they regularly get information from sources that they do not entirely trust. A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search. For example they might read Michael Moore because he is entertaining, while having low opinions of his credibility, or they might read articles mailed to them by friends.

@@

There is also evidence that a significant group of people are interested in checking information they read on the web. Several popular web sites are designed primarily to help users check information they read elsewhere. For example Snopes.com contains information about urban myths such as ``eskimos have many words for snow'' and Factcheck.org and Politifact.com investigate claims made by American political figures. According to Quantcast.com, Snopes has around five million unique visitors per month.

To check these assumptions, we circulated a survey among members of a local debate club, who we anticipated would be a good match for our Skeptical Reader and Activist personals. Of the 23 people who responded, 91\% said that they sometimes or often check information they read on a trusted site (64\% often, 27\% sometimes) and 91\% said that they sometimes or often check information by searching for other web pages about the same topic (74\% often, 17\% sometimes).

@@

@@

There are two key differences between Dispute Finder and these annotation tools: First, rather than allowing a user to express their own opinions about a topic, Dispute Finder instead requires a user who wants to promote a particular opinion to do so by linking to an article from a trusted source that argues for that opinion. Our interviews (Section~\ref{sec:interviews}) lead us to believe that most users would rather know that a trusted source disagrees with what is being written than that an unknown user disagrees.

The second key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate {\it text on a particular page} while Dispute Finder attempts to allow a user to annotate a {\it general claim, everywhere it appears on the web, however it is worded}. If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page. If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears. The closest annotation system to Dispute Finder in this respect is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.

Several Sensemaking, Decision Support, and Argumentation tools allow a user to annotate a document with structured information that they may then share with other users. TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that they extracted from them, and connecting these facts into a decision graph. ClaimSpotter~\cite{Sereno2005,Sereno2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document. Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts extracted from it. Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''. An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.

@@

There are also several tools that find pages write about the same topic with different slants, rather than looking at the specific claims a page makes. News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story. The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue. 
Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias. Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking. Newstrust allows users to rate news articles for quality and objectivity.

@@

\item[Highlighting disputed claims for users:] If we are to alert a user when they read disputed information, we need to be able to tell what text they are reading, and we need a way to inform them that this information is disputed. Ideally, this method should apply to as much of the information the user reads as possible, and be easy for a user to adopt. We also want to avoid distracting the user unnecessarily, while also making sure that they notice disputed claims that they would care about.

\item[Providing tools that help users interpret disputed claims:] Once a user has learned that a claim is disputed, it is likely that they will want to see information that will help them decide whether they should believe the claim and what other sources they should read. We want to help a user understand both {\it who} holds other points of view and {\it why} other people hold different points of view.

\item[Determining Trustworthy Sources:] What sources should we consider ``trustworthy'' in the sense that their opinions are worth presenting to the user, and things that they disagree with should be highlighted as disputed. There is a trade-off between showing a user sources that they will trust, and showing them sources that will expose them to a new point of view.
\end{description}

These challenges are not unique to dispute finder; indeed they apply to any tool that informs a user about disputed information and helps users interpret this disputed information.

In the rest of this section, we discuss the various alternative solutions that we explored for each of these problems, and our experiences with the approaches that we implemented and tested.

@@

Dispute Finder maintains a shared server-side database of known disputed claims. The browser extension highlights a text snippet if it believes that the snippet entails one of the claims in this database (Figure~\ref{snippet_claim_article}). Claims can either be added directly by users (Figure~\ref{add_claim}) or mined from web sites such as Snopes and Politifact that already maintain well curated databases of disputed claims,

This database should not contain contain everything that has ever been disputed by anyone. In some sense almost everything is disputed by someone on the web. There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would be so distracting as to be worthless. Similarly, there is little point spending effort rebutting claims that nobody believes. For example there is reliable evidence opposing the claim that the moon is made of cheese, but few people believe this claim is true. What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.

@@

One weakness of the automatic import approach is that the claims found on these sites are often phrased differently to the way they commonly appear on the web. For example many of the claims on Politifact are exact quotes such as ``One-third of the health care dollar goes to no such thing as health care; it goes to the insurance companies''. In practice, it is often necessary for users to enter several simple paraphrases for a claim before it can be widely recogonsized.

Dispute Finder also provides users means to add their own disputed claims using the Dispute Finder web interface (Figure~\ref{add_claim}). The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org. It first encourages the user to search the existing database to see if their claim already exists, and then allows them to create a new claim. When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing article. At the time of writing, users have added 557 claims, and 140 users have added at least one claim.

%The automatic import bootstraps Dispute Finder with a useful database of disputed claims without needing a large active user community, and the crowd-sourcing aspect allows users to clean up claims that were not phrased well when imported, and add claims that are not part of any of our input feeds.

@@

In future work, we hope to automatically find disputed claims on the web by looking for phrases like ``falsely claimed that X'' --- a similar techniques to that used by Hearst to find hyponyms~\cite{Hearst1992}, and then use context to help determine which phrases are likely to be making the same claim.

@@

Dispute Finder highlights a snippet if it thinks it entails the truth of a known disputed claim. This is complicated by the fact that a claim can be phrased in many different ways, and a snippet does not need to explicitly state a claim in order to entail its truth. For example ``I prefer margarine to butter because it is healthier'' entails ``margarine is healthier than butter''. Our implementation maintains a local copy of our claim database inside the browser extension and runs a simple textual entailment algorithm inside the browser to look for sentences that appear to entail known disputed claims.

There is a trade-off between precision and recall. We want to maximize the likelihood that Dispute Finder will highlight a snippet if it is making a known disputed claim, while minimizing the likelihood that it will highlight a snippet that is not making a known disputed claim. We implemented and tested four different approaches that represent different points along this trade-off:

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/mark_disputed.png}
	\caption{Explicit page marking: select the snippet and click ``this is disputed'' on the context menu.}
	\label{mark_disputed}
	\end{center}
\end{figure}

@@

\label{sec:explicit_mark}
\begin{description}
\item[Explicit page marking:] The user explicitly marks a snippet on a page by selecting the snippet, and selecting ``mark as disputed'' from a context menu (Figure~\ref{mark_disputed}).

\item[Bulk page marking:] The user uses a search interface to rapidly gather many snippets that contain similar phrases, and then selects those that they would like to mark (Figure~\ref{training}). The server uses Yahoo BOSS\footnote{http://developer.yahoo.com/search/boss} to search the web for snippets that resemble a paraphrase entered by the user.

\item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier. We used a simple Bayesian classifier with n-grams as features. The classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.  Once the classifier has been trained, the server uses it to refine which other results from Yahoo BOSS should be marked (Figure~\ref{training}).

@@

Explicit page marking has the highest precision, but the poorest coverage. Since a user is looking at the page in its entirety, they can read the snippet in context and make a good judgment about whether the snippet is indeed making the claim. However the manual effort required per page makes it difficult for this approach to scale. We also found that it can also be hard to motivate a user to mark snippets if they think that it is unlikely that another user with the Dispute Finder extension will read exactly this page. This same problem has hindered the adoption of numerous web page annotation tools.

@@

Client side entailment gets the most coverage. Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined. This is particularly important for news pages, which are frequently read only a few minutes after they are posted. Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and intranet sites.

A further advantage of the client-side approach is that it avoids the need for the client to give the server any information about what pages the user is browsing. The list of all URLs and snippets that make disputed claims is too large and updates too frequently for it to be practical for the client to store it locally, so the client instead asks the server for information about each URL the user browses, reducing user privacy. By contrast, the list of paraphrases is small enough and changes slowly enough that the client can maintain its own local copy of the database, removing the need for the client to tell the server what pages the user is browsing. As our database grows bigger, it will of course become more challenging to maintain a local copy in the browser extension.

@@

LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist. Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, inferring inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2001,Dinu2009,Bhagat2009}, and using Bayesian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}. Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions. Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.

@@

Other authors have used similar algorithms to find repeated information on the web. Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, and duplicate-detection is often used to clean up web searches~\cite{Theobald2008}. MemeTracker~\cite{Backstrom2009} looks for phrases shared by multiple news stories, accounting for minor variations, and uses this to track the way that news flows between traditional news sources and blogs.

@@

The Dispute Finder Firefox extension uses two mechanisms to inform a user when information on the page they are reading is disputed. It highlights any disputed snippets in red, and it displays a notification bar (Figure~\ref{highlight_bar}).

The notification bar alerts the user that they should look out for highlighted snippets. Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors.} particularly if the user is color blind. The notification bar also allows a user to step through the highlighted snippets on the page.

The highlights show a user {\it which snippets} Dispute Finder believes are making disputed claims. A user can see whether the highlights are in the text that they are reading and ignore disputed snippets in text that they are not interested in - such as user comments. The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it is not making. In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the ``report incorrect highlighting'' button from the popup interface.

@@

When a user clicks on a highlighted snippet, Dispute Finder displays a popup pane with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read. In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{article_list}). We also implemented and tested an interface that contained a user-editable argumentation graph; however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.

@@

\begin{description}
\item[Convenience:] A user may not have the patience to search for a good source of information about a claim. 
\item[Moderation:] We only want Dispute Finder to highlight a claim if we know that there is credible evidence for an alternative point of view. By storing the evidence for alternative points of view inside Dispute Finder, it becomes easier for a moderator user to evaluate whether a claim is sufficiently disputed that it belongs in the Dispute Finder database.
\item[Filtering:] Although we have not implemented this feature currently, we think it could be useful to build a model of what sources a user trusts and only highlight a disputed claim if a source that the user trusts argues against it.
\end{description}

@@

\begin{description}
\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph. This graph is inspired by IBIS~\footnote{Issue Based Information System} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}. Each claim is linked to claims that represent alternative points of view, and claims that support that point of view. Each claim also has a list of articles that argue in favor of that claim (Figure\ref{popup_graph})

@@

\section{Evaluation}
\label{sec:interviews}
\label{user-studies}
